\documentclass[12pt, a4paper]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.7cm,top=1.7cm,right=1.7cm,bottom=2cm]{geometry}
\usepackage{setspace}
\usepackage{xurl}
\pagenumbering{gobble}
\setstretch{1.25}
%by: Aline R. Antunes

\hypersetup{colorlinks=true, urlcolor=blue}

\begin{document}
% \onehalfspacing
\fontfamily{ppl}\selectfont

\begin{center}
	\Large\textbf{Muhammad Usaid Rehman}\\
	\hrulefill
\end{center}

\begin{center}
	\href{mailto:rehman.usaid@gmail.com}{\texttt{rehman.usaid@gmail.com}} \textbullet \ +923451440433 \textbullet \ \href{https://github.com/m-usaid99}{GitHub} \textbullet \ \href{https://www.linkedin.com/in/muhammad-usaid-rehman-aa8b64202/}{LinkedIn} \textbullet \href{https://musaid-rehman.vercel.app}{Portfolio}
\end{center}

\begin{center}
	\large\textbf{Education}
\end{center}

\textbf{University of Windsor}  \hfill Windsor, ON

MSc. Computer Science [Incomplete]  \hfill \textit{Aug 2022 -- Dec 2023}

Research Focus: Cryptography \& Computational Mathematics


% Relevant Coursework: Computational Mathematics, Cryptography, Privacy \& Security, Computational Gemoetry

\vspace{12pt}
\textbf{Habib University} \hfill Karachi, Pakistan

BSc. Computer Science, Minors: Mathematics \& South Asian Music \hfill \textit{Aug 2018 -- May 2022}

Scholarship: 70\% Excellence Scholarship awarded for A-Level results.

GRE Score: 318, TOEFL iBT: 112

\vspace{12pt}
% \textbf{Cedar College} \hfill	Karachi, Pakistan 
\textbf{Certifications:}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item FrontEnd Engineering (Career Path) -- Codecademy \hfill [\href{https://www.codecademy.com/profiles/candyclaws99/certificates/2682884a0719474f96407efe432fdd87}{Certificate Link}]
	\item Create a Backend App with Javascript (Skill Path) -- Codecademy \hfill [\href{https://www.codecademy.com/profiles/candyclaws99/certificates/5cb678013709022f5b908913}{Certificate Link}]
	\item  Design Databases with PostgreSQL (Skill Path) -- Codecademy \hfill [{\href{https://www.codecademy.com/profiles/candyclaws99/certificates/5f64e3b492de0000131ecbe0}{Certificate Link}}]
	\item Fundamentals of Cybersecurity (Skill Path) -- Codecademy \hfill [\href{https://www.codecademy.com/profiles/candyclaws99/certificates/06984a073b064e61879cca3e82a9b3d2}{Certificate Link}]
	\item Applied Data Science Specialization (IBM) -- Coursera \hfill [\href{https://coursera.org/share/d030e4f8979b8718d0b067ae3f467d33}{Certificate Link}]
\end{itemize}
% A Levels \hfill \textit{Sep 2016 -- May 2018}

% Subjects: Physics (A), Chemistry (A), Mathematics (A), Further Mathematics (A)

% SAT: 1480, TOEFL iBT: 112

% \vspace{12pt}

\begin{center}
	\large\textbf{Experience}
\end{center}

\textbf{Realtor Buddy} \hfill (Remote)

\textbf{FrontEnd Developer (Contract)} \hfill \textit{April 2024 -- May 2024}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Designed a user-interface/user-experience for a landing page (\url{https://www.realtor-buddy.com}) for a product meant for realtors in the United States.
	\item Wireframed user-interface for both desktop and mobile versions of the website via Figma.
	\item Developed complete front-end using React, incorporating best practices for long-term maintainability and helped implement subscription model and incorporating third-party API in both the backend and frontend to handle subscriptions.
\end{itemize}

\vspace{16pt}
\textbf{University of Windsor} \hfill Windsor, ON

\textbf{Graduate Teaching Assistant} \hfill \textit{Sep 2022 -- Dec 2022}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Assisted faculty with COMP 4150: Advanced and Practical Database Systems, and COMP 4670: Network Security.
	\item Designed, conducted and graded weekly labs, graded weekly assignments, quizzes, and exams in a timely manner and conducted regular office hours for individual instruction.
	\item Assisted with course organization, liaised with faculty and students, and proctored exams.
\end{itemize}

\vspace{12pt}
\textbf{World Wildlife Fund Pakistan} \hfill (Remote)

\textbf{Machine Learning Intern} \hfill \textit{Summer 2021}

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Co-developed a bird image recognition model as proof-of-concept for future ecology use.
	\item Scraped the internet using BeautifulSoup and also manually, to collect images of birds and implemented a data preprocessing pipeline to construct training and testing sets.
	\item Experimented with various Convolutional Neural Networks (CNNs), including ResNet50 to obtain 90\% accuracy upon testing.
	\item Produced a final report detailing the model performance, deployment guide, and future enhancements.
\end{itemize}

\vspace{12pt}
\textbf{Habib University} \hfill Karachi, Pakistan

\textbf{Teaching Assistant} \hfill \textit{Sep 2020 -- May 2022}

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Worked as a teaching assistant for the courses CS 440: Design \& Analysis of Algorithms, CS 212: Nature of Computation, CS 202: Engineering Mathematics, CS 102: Calculus II.
	\item Conducted weekly tutorials to revise concepts introduced in class.
	\item Graded quizzes, assignments and conducted office hours to provide individual assistance.
\end{itemize}

%%%%%%%%%%%%%%% PROJECTS %%%%%%%%%%%%

\begin{center}
	\large\textbf{Projects}
\end{center}
\textbf{A Novel Approach to Protein Complex Identification \\ via Ensemble Clustering}	\hfill [\href{https://github.com/hurryingauto3/PPI-Complex-Prediction}{GitHub}]
\begin{center}
	\parbox{0.9\linewidth}{
		Final Year Project for BSc. Computer Science at Habib University. Conducted an extensive literature review and implemented a novel clustering algorithm to detect protein complexes in an interaction network, using deep learning, genetic algorithms and graph-theoretical algorithms.

		\textit{Python, Numpy, Seaborn, Pytorch, \LaTeX}
	}
\end{center}

% \textbf{MultiStage Optimization for Combinatorial Optimization Problems} \hfill [\href{https://github.com/m-usaid/Research-CombinatorialOptimization-DynamicProgramming}{GitHub}]
% \begin{center}
% 	\parbox{0.9\linewidth}{
% 		Worked on an independent research project in Summer 2021 under the guidance of Dr. Shahid Hussain to implement a chain of multistage optimization algorithms on matrix multiplication and other combinatorial problems. Implemented the algorithm in C++ and analyzed results empirically using Python.
%
% 		\textit{C++, Bash, Python, \LaTeX}
% 	}
% \end{center}



\textbf{ExpenseMate -- Portfolio Project}	\hfill [\href{https://github.com/m-usaid99/ExpenseMate}{GitHub}]
\begin{center}
	\parbox{0.9\linewidth}{
		A full-stack \href{https://expensemate.vercel.app}{personal finance management dashboard}, designed using React/Redux + Material UI. Stores data in a MongoDB database hosted on MongoDB Atlas accessed through a rigorously tested RESTful API. Visualizes, summarizes and presents expense and income history/trends using charts and tables for easy monitoring of financial health.

		\textit{React, Redux, Material UI, Express, Mongoose, Jest, Docker, Swagger}
	}
\end{center}

% \textbf{Agent-Based Modelling of Slime Mold} \hfill {\href{https://github.com/hurryingauto3/CS262-Computational-Social-Science}{[GitHub]}}
% \begin{center}
%     \parbox{0.9\linewidth}{
%         Term project for CS 262: Computational Social Science. Implemented an agent-based-model of slime mold (\textit{P. polycephalum}) in order to simulate its behavior. Conducted a statistical analysis of a number of simulations and submitted our findings in a report. 
%     \textit{NetLogo, Python, \LaTeX}
%     }
% \end{center}

\textbf{ Spotify Jammming -- Portfolio Project} \hfill [\href{https://github.com/m-usaid99/spotify-jammming}{GitHub}]
\begin{center}
	\parbox{0.9\linewidth}{
		Portfolio project -- \url{https://spotify-jammming.vercel.app} -- using React.js, styled with Emotion. Wireframed, designed, and completed a project to practice and improve web development skills. Worked with the Spotify API to search tracks, display album art \& album details; and save a playlist to users' Spotify account.

		\textit{JavaScript, React.js, Emotion, HTML, CSS, Figma}
	}
\end{center}

\newpage
\begin{center}
	\large\textbf{Skills \& Interests}
\end{center}

\textbf{Programming Languages:} Python (multiple libraries including SageMath), JavaScript, TypeScript, C, C++, Rust, Bash, Prolog, R

\textbf{Web Development:} \textit{Frontend:} React, Redux, Angular, Emotion, p5.js + WebGL, HTML, CSS

\textit{Backend}: Node.js, Express, Django, Flask

\textit{Tools:} npm, webpack, Jest, react-testing-library, Babel, Vite

\textit{UI/UX Design:} Chakra UI, Material UI, Figma, WireFraming

\textbf{Databases:} MongoDB + Mongoose, MySQL, PostgreSQL

\textbf{AI/ML \& Data Science:} Scikit-learn, Pandas, TensorFlow, Pytorch, Plotly Dash

\textbf{DevOps \& Tools:} Git/GitHub, testing via Mocha + Chai, Linux, CI/CD (GitHub Actions)

\textbf{Theoretical Skills \& Interests:} Design \& Analysis of Algorithms, Natural Computing, Agent-Based Modelling, Theory of Computation, Cryptography, Pure Mathematics

\end{document}
